Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
add difficult list tasks

\begin{table}
\centering
\begin{tabular}{lll}
  \toprule
  Name & Input & Output \\\midrule
  add-3 & [1\, 2\, 3\, 4] & [4\, 5\, 6\, 7] \\
  append-4 & [7\, 0\, 2] & [7\, 0\, 2\, 4] \\
  len & [3\, 5\, 12\, 1] & 4 \\
  range & 3 & [1\, 2\, 3] \\
  has-2 & [4\, 5\, 7\, 4] & \code{false} \\
  has-head-in-tail & [4\, 5\, 7\, 4] & \code{true} \\
  repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
  drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
  \bottomrule
\end{tabular}
\caption{Sample tasks from our list function domain. %% We used 15 input/output
  %% examples for each task to reduce ambiguity in the task's function,
  %% ensuring solutions achieve the desired concept.
}
\label{listexamples}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{lll}
  \toprule
  Name & Input & Output \\\midrule
  append-4 & [7\, 0\, 2] & [7\, 0\, 2\, 4] \\
  len & [3\, 5\, 12\, 1] & 4 \\
  has-2 & [4\, 5\, 7\, 4] & \code{false} \\
  repeat-2 & [7\, 0] & [7\, 0\, 7\, 0] \\
  drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
  count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
  rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
  pow-3 & [10\, 4\, 13] & [1000\, 64\, 2197] \\
  keep-mod-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
  \bottomrule
\end{tabular}
\caption{Sample tasks from our list function domain. %% We used 15 input/output
  %% examples for each task to reduce ambiguity in the task's function,
  %% ensuring solutions achieve the desired concept.
}
\label{listexamples}
\end{table}
